% 06Holonomic.tex

\subsection{6.1. The Robenius Integrability Condition}

Can one always find a surface orthogonal to a family of curves in $\mathbb{R}^3$?

\subsection{6.2. Integrability and Constraints}

\subsection{6.3. Heuristic Thermodynamics via Caratheodory}

Can one go adiabatically from some state to any nearby state?

\subsubsection{6.3a. Introduction}



\subsubsection{6.3b. The First Law of Thermodynamics}

Consider system of regions of fluids separated by ``diathermous'' membranes \\
\phantom{\quad \, } allow only passage of heat, not fluids \\

assume system connected \\
assume each state in thermal equilibrium

Let $p_i,v_i$ (uniform) pressure and volume of $i$th region \\
\phantom{\quad \, } at thermal equilibrium, ``equations of state'' $p_iv_i = n_iRT_i$ \\
\phantom{\quad \quad \, } $p_i v_i = n_iRT_i$ eliminate all but 1 pressure
\[
\Longrightarrow p_1, v_1,v_2, \dots v_n
\]
assume globally defined energy function $U$

path in $M^{n+1}$ represents sequence of states each in equilibrium, i.e. assume very slow changes in time, quasi-static irreversible processes, e.g. ``stirring'' \\
on $M$, $\text{dim}{M} = n+1$, assume $\exists \, $ work 1-form $W$, work done by system 
\[
W = p_i dv_i = p_i(U,v_1\dots v_n)dv_i \quad \quad \, i=1 \dots n 
\]
heat 1-form, heat added or removed from system, assume $Q \neq 0$
\[
Q = \sum_{i=0}^n Q_i(U,v_1 \dots v_n) dv_i \quad \, (v_0 = U)
\]

1st. law of thermodynamics 
\[
dU = Q-W
\]
energy conservation 

\subsubsection*{6.3c. Some Elementary Changes of State}

1. Heating at constant volume. 

\phantom{\quad \, } path $\gamma_I \in M$, $\text{dim}M = n+1$ s.t. $dv_1 = \dots = dv_n =0$.  $W=0$
\phantom{\quad \, } $dU = Q_0 dU$.  $\dot{\gamma}_I = c_0 \frac{\partial}{ \partial U}$

2. Quasi-static adiabatic process.  No heat exchanged,
\[
Q(\dot{\gamma}_{\text{II}}) = 0 \quad \, \text{ so } dU = -W
\]

3. Stirring at constant volume adiabatic, but not quasistatic  \\
\phantom{\quad \, } $Q,W$ makes no sense but \\
\phantom{\quad \, } work is being done by (or on) system, $U(y') - U(x)$, difference of internal energy \\
assume connected mechanical manifold $V$, $\text{dim}V =n$ \\
\phantom{assume } diff. $\pi:M \to V$ \\
\phantom{assume diff} $\pi$ onto \\
\phantom{assume diff} $\pi_*$ onto \\
\phantom{assume diff} $\pi$ submersion

By main thm. on submanifolds of Sec. 1.3d, \\
\phantom{\quad \, } if $v\in V$, then $\pi^{-1}(v)$ 1-dim. embedded submanifold of $M$ \\
\phantom{\quad \quad \, } assume $\forall \, \pi^{-1}(v)$ connected, we're assuming given any pair of states \\
\phantom{\quad \quad \quad \, } lying on $\pi^{-1}(v)$, 1 of them can be obtained by other by ``heating at constant volume''

assume $W$ on $M$ is $0$ when $\left. W \right|_{\pi^{-1}(v)} =0$ \\
on the other hand, $Q \neq 0$ on $\pi^{-1}(v)$; $dU = Q \neq 0$ (first law) \\
\phantom{\quad \, } $(U,v^1 \dots v^n)$ local coordinate system for $M$ ($U$ global coordinate)

\subsubsection{6.3d. The Second Law of Thermodynamics} 

cyclic process starts and ends at the same state

Kelvin 2nd. law of thermodynamics \\
\phantom{\quad \, } $\nexists $ quasistatic cyclic process can $Q$ converted entirely into $W$  \\

Caratheodory (1909) 2nd. law of thermodynamics \\
\phantom{\quad \, } $\forall \, $ neighborhood $N \ni $ state $x$, $\exists \, y$ not accessible from $x$ via quasistatic adiabatic paths, i.e. paths s.t. $Q=0$



